---
title: "Getting Started with iopqualr"
author: "Clinbay"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Getting Started with iopqualr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, cache = FALSE, fig.width = 6, fig.height = 4.5)
```

# Introduction

*iopqualr* is an R package designed for creating automated Installation Qualification (IQ), Operational Qualification (OQ), and Performance Qualification (PQ) reports for R environments in regulated industries. It generates reports as PDF or HTML, ensuring and proving the accuracy and reproducibility of R program outputs, essential for compliance with validation and quality assurance requirements.

For detailed guidance on using R in a regulated environment and custom validation services, you can contact ClinBAY or check the [R Validation Hub](https://www.pharmar.org/overview/) for compliance guidelines.

## Installation

The package can be installed from CRAN or directly from a GitHub repository. Here's how you can install the iopqualr package from various sources:

### From CRAN

```{r, eval=FALSE, echo=TRUE}
install.packages("iopqualr", dependencies = TRUE)
```

### From GitHub

```{r, eval=FALSE, echo=TRUE}
# Install the devtools package if not present
install.packages("devtools")
devtools::install(repo="https://github.com/ClinBAY/R-IQ-OQ-PQ-Validation", dependencies = TRUE)

```

### From a Local Folder or Zip File

It is also possible to install the package from a local source, such as a folder or a .zip file:

- Rtools is requisite for Windows users to build from source.
- The path specified in the install command should be the actual path to the .zip or folder.

```{r, eval=FALSE, echo=TRUE}
# Install Rtools from https://cran.r-project.org/bin/windows/Rtools/
install.packages("devtools")
# For a .zip file:
devtools::install("C:/path_to_zip/name_of_zip.zip", dependencies = TRUE)
# For an uncompressed local folder:
devtools::install("C:/path_to_folder/", dependencies = TRUE)
```

## Loading the package

After installation, load the package into the R session:

```{r, echo=TRUE}
library(iopqualr)
```

## Creating an Initial YAML File

The package requires a YAML file defining the configuration for the qualification reports. To assist with creating this YAML file, *iopqualr* provides an interactive function:

```{r, eval=FALSE, echo=TRUE}
iop_input_helper()
```

This will guide you through setting up the necessary configurations.

## Generating Reports

Using the YAML file created with `iop_input_helper()`, you can generate the qualification report by running `iop_create_report()`. Here is how you call the function with the necessary parameters:

```{r, eval=FALSE, echo=TRUE}
# Ensure the settings_file (YAML), input_directory, settings_directory, and test_outputs_directory paths are correctly set
# Also, specify whether you desire an HTML report with html_report parameter
iop_create_report(
  settings_file = "<yaml_filename>",
  settings_directory = "<settings_directory>",
  input_directory = "<input_directory>",
  test_outputs_directory = "<output_location>",
  html_report = FALSE # Or TRUE for an HTML report
)
```

## Obtaining Further Assistance

For more information and advanced features, please refer to the official documentation for the iopqualr package and the R Validation Hub for additional resources on complying with R environment validation in regulated industries.

## Conclusion

This vignette provides you with the knowledge to install the iopqualr package and generate a comprehensive report to qualify your R environment, which is indispensable in regulated settings.

# References

- Official *iopqualr* GitHub repository and issue tracker: [User documentation](https://github.com/ClinBAY/R-IQ-OQ-PQ-Validation) | [Issue tracker](https://github.com/ClinBAY/R-IQ-OQ-PQ-Validation/issues)
- R Validation Hub: [Overview](https://www.pharmar.org/overview/)
